%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
%\copyrightyear{2018}
\acmYear{2020}
%\settopmatter{printacmref=false}
%\setcopyright{acmlicensed}
%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}
%\usepackage{cite}
%\usepackage[bottom]{footmisc}
\usepackage{enumitem}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
%\usepackage{hyperref}
%\usepackage{algorithmic}
\usepackage{algcompatible}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{multirow} 
\usepackage{amsthm}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{amsmath}

\usepackage{xspace}
\usepackage{caption}
%\captionsetup[figure]{font=small,labelfont=small}
\usepackage{subcaption}
%\captionsetup[subfigure]{font=scriptsize,labelfont=scriptsize}
%\usepackage[color]{changebar}
%\cbcolor{red}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{exmp}{Example}[section]
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\input{defs}
\hypersetup{draft}

\begin{document}
\title{\system: Crypto-Assisted Differential Privacy on Untrusted Servers}
\author{}
\begin{abstract}
Differential privacy (DP) has steadily become the de-facto standard for achieving privacy in data analysis. It is typically implemented either in the ``central'' or ``local'' model. %In the former, a trusted centralized server collects the records \textit{in the clear} from the data owners and outputs differentially private statistics; while in the latter, the data owners individually randomize their inputs to ensure differential privacy.  
The local model has been more popular for commercial deployments as it does not require a trusted data collector (unlike the central model). This increased privacy, however, comes at the cost of strictly lower accuracy and restricted algorithmic expressibility as compared to the central model. 

In this work, we propose, \system, a  system and programming framework that (1) achieves the accuracy guarantees and algorithmic expressibility of the central model (2) without any trusted data collector like in the local model. \system achieves the ``best of both worlds'' by employing two non-colluding untrusted servers that run DP programs on encrypted data from the data owners. Although straightforward implementations of DP programs using secure computation tools can achieve the above goal theoretically, in practice they are beset with many challenges like poor performance, tricky security proofs etc. To this end, \system allows data analysts to author logical DP programs that are automatically translated to secure protocols that work on encrypted data. These protocols ensure that the untrusted servers learn nothing more than the noisy outputs, thereby guaranteeing $\epsilon$-DP for all \system programs.  \system
supports a rich class of DP programs that can be expressed via a small set of transformation and measurement operators followed by arbitrary post-processing. Further, we propose performance optimizations leveraging on the fact that the output is noisy. We demonstrate \system's feasibility for practical DP analysis with extensive empirical evaluations on real datasets. 
\end{abstract}
\eat{\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002979.10002981.10011745</concept_id>
<concept_desc>Security and privacy~Public key encryption</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002978.10002991.10002995</concept_id>
<concept_desc>Security and privacy~Privacy-preserving protocols</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Security and privacy~Public key encryption}
\ccsdesc[300]{Security and privacy~Privacy-preserving protocols}}
%\begin{IEEEkeywords}
\keywords{Crypto Service Provider, LHE, Two Server Model}
 \settopmatter{printfolios=true}
\maketitle
%\end{IEEEkeywords}
\input{Intro_new}
\input{Outline_Section2.tex}
%\input{SMCvsCryptE}
\input{background}
\input{overview}
\input{primitives}
\input{programexamples.tex}
\input{im}
\input{optimizations}
\input{Sec-theorem.tex}
\input{evaluation}
\input{briefRelatedWork.tex}
\input{conclusion}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{abbrv}
\bibliography{references.bib}

\appendix
\input{appendix}
\end{document}
